\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Harshit Mangal} \\ \vspace{3pt}
    \small +91-7413021531 $|$ 
    \href{mailto:mangalharsh54@gmail.com}{\underline{mangalharsh54@gmail.com}} $|$ 
    \href{https://linkedin.com/in/harshit-mangal}{\underline{linkedin.com/in/harshit-mangal}} $|$ 
    \href{https://github.com/harshitmangal}{\underline{github.com/harshitmangal}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MBM University}{Jodhpur, Rajasthan}
      {Bachelor of Technology in Information Technology $|$ CGPA: 7.5 (Ongoing)}{\textnormal{Aug. 2023 -- May 2027}}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{ShopSphere} $|$ \href{https://flipcart-clone-mu.vercel.app/}{\underline{Live Link}} $|$ \href{https://github.com/HarshitMangal/Flipcart-Clone}{\underline{GitHub}} $|$ \emph{MongoDB, Express, React, Node.js, Redux}}{2026}
      \resumeItemListStart
        \resumeItem{Developed a full-stack e-commerce platform integrating a stateful \textbf{Google Gemini 2.5 Flash AI Assistant} for catalog recommendation queries, backed by a \textbf{fail-safe Redis caching layer} reducing query response latency by 90\% to <2ms.}
        \resumeItem{Implemented secure user authentication and seller registration leveraging \textbf{JWT (JSON Web Tokens)} and Google OAuth, designing a custom \textbf{Seller Onboarding Flow} with GSTIN verification.}
        \resumeItem{Integrated a backend-verified checkout flow using \textbf{Razorpay Payments API} with SHA-256 HMAC cryptographic signature checks to prevent client-side transaction tampering.}
        \resumeItem{Built a social \textbf{Group Buying (Team Buy) system} validating user team completions to dynamically apply checkout discount rates.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Haven} $|$ \href{https://major-project-wht3.onrender.com/}{\underline{Live Link}} $|$ \href{https://github.com/HarshitMangal/major_project}{\underline{GitHub}} $|$ \emph{EJS, Node.js, Express, MongoDB}}{2025}
      \resumeItemListStart
        \resumeItem{Developed a full-stack property rental platform using EJS for server-side rendering and Node.js/Express.js backend.}
        \resumeItem{Implemented secure user authentication, property listings creation, and booking workflows with MongoDB data persistence.}
        \resumeItem{Designed RESTful API endpoints for handling property filters, ratings, and customer reviews.}
        \resumeItem{Built a responsive UI ensuring smooth user experience across devices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Frontend Web Development Intern}{June 2025 -- July 2025}
      {CodTech IT Solutions Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Independently built 3 production-grade projects: a real-time chat application, an interactive quiz app, and a responsive e-learning platform UI — delivering all within a 2-month timeline.}
        \resumeItem{Implemented cross-browser compatible, mobile-first UI components using HTML, CSS, and JavaScript; integrated REST APIs and followed Git-based collaborative workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages}: Python, C++, C, Java, JavaScript, SQL \\
     \textbf{Web \& Frameworks}: HTML, CSS, React, Redux Toolkit, Node.js, Express, Tailwind CSS, EJS, Mongoose, JWT \\
     \textbf{Databases}: SQLite, MySQL, MongoDB, Redis \\
     \textbf{Developer Tools \& Cloud}: Git, GitHub, Docker (Basics), Postman, Render, Vercel, Heroku, Linux, POSIX \\
     \textbf{CS Fundamentals}: Data Structures \& Algorithms, Object-Oriented Programming (OOPs), Database Management Systems (DBMS), Operating Systems (OS), RESTful APIs, MVC Architecture
    }}
 \end{itemize}


%-----------CODING PROFILES-----------
\section{Coding Profiles}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{LeetCode} $|$ \href{https://leetcode.com/u/Harshit_mangal/}{\underline{Profile}}}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{1100+ Problems Solved $|$ Contest Rating: 1747}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{GeeksforGeeks} $|$ \href{https://www.geeksforgeeks.org/profile/mangalhaqw0dinko}{\underline{Profile}}}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{1000+ Problems Solved $|$ College Rank 1}
        \resumeItem{Completed 160 Days of Problem Solving Challenge (2025)}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{InterviewBit} $|$ \href{https://www.interviewbit.com/profile/}{\underline{Profile}}}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Consistent DSA practice across arrays, trees, graphs, and dynamic programming}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
      \href{https://media.geeksforgeeks.org/courses/certificates/22a599fc4a5676f802aa4a2ee4cc3c7f.pdf}{\underline{160 Days of Problem Solving}} -- GeeksforGeeks (2025) \\ \vspace{2pt}
      \href{https://www.hackerrank.com/certificates/227251652361}{\underline{HackerRank Basic Certification}} -- HackerRank (2026) \\ \vspace{2pt}
      \href{https://www.hackerrank.com/certificates/9fe36f33fe64}{\underline{HackerRank Certification}} -- HackerRank (2026)
    }}
  \end{itemize}

\end{document}
